CRUSE to Safe Cycling in Ireland

### 2023-09-25 paper.qmd
Update formats, not latex
Update description of user stories figure

# Uncomment for draft versions:
format: 
  html: default
  docx: default
  pdf: default

@@

For non-professional users, the tool provides a simple interface to explore the cycling potential of the network.
By providing a single landing page that is suitable for both professional and non-professional users, the tool aims to facilitate communication between these groups.

```{mermaid}
%%| fig-width: 100%
%%| fig-cap: User stories for the CRUSE tool
%%| label: fig-user-stories
graph LR
    A(Professional user) --> B[CRUSE landing page]
    B --> C[CRUSE national map]
    C --> D[CRUSE county map]
    D --> F[Full county map]
    D --> CS[County statistics]
    D --> Q[Quiet and fast route networks]
    D --> DD[Data downloads]
    DD --> EX{External tools}
    X(Non-professional user) --> Y[CRUSE landing page]
    Y --> Z[CRUSE national map]
    Z --> R[CRUSE county level results]
    Z --> E(Exploration)
    R --> E
    E --> COMS{Communication}
```

@@

@@

>>>>

# Uncomment for draft versions:
format: 
  html: default
  # docx: default
  # pdf: default

@@

For non-professional users, the tool provides a simple interface to explore the cycling potential of the network.
By providing a single landing page that is suitable for both professional and non-professional users (such as an advocate or parent interested in safe routes to school), the tool aims to facilitate communication between these groups.

```{mermaid}
%%| fig-width: 100%
%%| fig-cap: Hypothetical user stories for the CRUSE tool illustrating that it can be used in different ways by different user groups.
%%| label: fig-user-stories
graph LR
    A(Professional user) --> B[CRUSE landing page]
    B --> C[CRUSE national map]
    C --> D[CRUSE county map]
    D --> F[Full county map]
    D --> CS[County statistics]
    D --> Q[Quiet and fast route networks]
    D --> DD[Data downloads]
    DD --> EX{External tools}
    X(Non-professional user) --> Y[CRUSE landing page]
    Y --> Z[CRUSE national map]
    Z --> R[CRUSE county level results]
    Z --> E(Exploration)
    R --> E
    E --> COMS{Communication}
```

@@

The main result of the CRUSE project is a new and open access web application and dataset on current and potential future cycling levels in Ireland, with evidence provided at county and route segment levels.
Like the PCT on which CRUSE builds, a key feature of the results is that they are systematic and available for all counties, and most routes on which cycling is permitted, in Ireland.

## National results {#sec-national-results}

The CRUSE tool provides estimates of cycling potential at the national level, as shown in @fig-national-results.

@@

## Local results

To illustrate the results in urban areas, we took the top 4 cities in Ireland by population: Dublin, Cork, Limerick and Galway.
The results for these cities are presented in @fig-city-results.

```{r}
# Results for one city

```
